---
title: "Function"
output: github_document
---

```{r}
library(tidyverse)
library(rvest)
```
My forst function
```{r}
x_vec = rnorm(25, mean = 5, sd = 3)
(x_vec - mean(x_vec)) / sd(x_vec)

z_score = function(x) {
  z = (x - mean(x)) / sd(x)
  z
}

z_score(x_vec)
```
what the fucntion can;t do
```{r}
z_score(3)
z_scores("my name is jeff")
z_score(c(TRUE, FALSE, TRUE, TRUE))
```
TRUE AND FALSE statementas are logical, R calcualting it as 1 and 0s. We dont wnat that. SO we need to fix the funtion iwth a conditional command, 
```{r}
x_vec = rnorm(25, mean = 5, sd = 3)
(x_vec - mean(x_vec)) / sd(x_vec)

z_score = function(x) {
  if (!is.numeric(x)) {
    stop("Argument must be numeric") } 
  else if (length(x) == 1) {
    stop("Z scores cannot be computed for length 1 vectors")  
    }
  z = (x - mean(x)) / sd(x)
  z
}

z_score(3)
z_scores("my name is jeff")
z_score(c(TRUE, FALSE, TRUE, TRUE))
```
Now the above command are sjhowing errors.

##Multiple outputs

```{r}
mean_and_sd = function(x) {
  if (!is.numeric(x)) {
    stop("Argument must be numeric") } 
  else if (length(x) == 1) {
    stop("Z scores cannot be computed for length 1 vectors")  
    }
  mean_x = mean(x)
  sd_x = sd(x)
  
  tibble(
    mean = mean_x,
    sd = sd_x
  )
}
```

```{r}
x_vec = rnorm(100)
mean_and_sd(x_vec)
```
It works!


## Multiple inputs
Now we are going to incoportae the rnorm into the function
```{r}
sim_data <- 
  tibble(
    x = rnorm(100, mean = 4, sd = 3)
  )

sim_data %>% 
  summarize(
    mean = mean(x),
    sd = sd(x)
  )


```

now a function taht does the same thing
```{r}

sim_mean_sd = function(samp_size, mu, sigma){
  sim_data <- 
  tibble(
    x = rnorm(n = samp_size, mean = mu, sd = sigma)
  )

sim_data %>% 
  summarize(
    mean = mean(x),
    sd = sd(x)
  )
}

sim_mean_sd(100, 6, 3)
sim_mean_sd(samp_size = 100, mu = 6, sigma = 3)
```
here the function is using assumption of positional matching. We can also use named matching. 


##Web scrapping

```{r}
url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=1"

dynamite_html = read_html(url)

review_titles <-  
  dynamite_html %>%
  html_nodes(".a-text-bold span") %>%
  html_text()

review_stars <-  
  dynamite_html %>%
  html_nodes("#cm_cr-review_list .review-rating") %>%
  html_text() %>%
  str_extract("^\\d") %>%
  as.numeric()

review_text <- 
  dynamite_html %>%
  html_nodes(".review-text-content span") %>%
  html_text() %>% 
  str_replace_all("\n", "") %>% 
  str_trim()

reviews <- tibble(
  title = review_titles,
  stars = review_stars,
  text = review_text
)
```
(str_trim trims off whoet spaces. )

WHat about the next page? We will need to do it again! Too difficult, We need a function
```{r}
read_page_reviews = function(url) {

dynamite_html = read_html(url)

review_titles <-  
  dynamite_html %>%
  html_nodes(".a-text-bold span") %>%
  html_text()

review_stars <-  
  dynamite_html %>%
  html_nodes("#cm_cr-review_list .review-rating") %>%
  html_text() %>%
  str_extract("^\\d") %>%
  as.numeric()

review_text <- 
  dynamite_html %>%
  html_nodes(".review-text-content span") %>%
  html_text() %>% 
  str_replace_all("\n", "") %>% 
  str_trim()

reviews <- tibble(
  title = review_titles,
  stars = review_stars,
  text = review_text
) 

reviews
}


dynamite_url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=1"

read_page_reviews(dynamite_url)
```



lets read a few pages now 

```{r}
dynamite_url_base = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber="

dynamite_urls = str_c(dynamite_url_base, 1:5)

all_reviews <- 
bind_rows(
  read_page_reviews(dynamite_urls[1]), 
  read_page_reviews(dynamite_urls[2]),
  read_page_reviews(dynamite_urls[3]),
  read_page_reviews(dynamite_urls[4]),
  read_page_reviews(dynamite_urls[5])
)


```





